Stochastic blockmodeling of relational event dynamics

### 2012-11-03 docs/submission.tex
Add cutom version of results tables and add new multicol headers.
Modify Figure 4 to focus on different clusters.
Add outline around clusters that we use for zoom in.

Figure \ref{fig:parmats} uses a fitted model to provide an example of the differences in the dynamics that can exist between two groups of dyads with similar rate of occurrence.  In this particular example we used the University data set and fit the proposed model with an intercept $s_0$, $\texttt{ab-ba}$ effects $s_1$, and $\texttt{ab-by}$ effects $s_3$. {\color{red} In Figure \ref{fig:parmats}a we show the observed number of times each dyadic event occurred over the course of the dataset.   The rows and columns have been sorted according to block membership.  In Figure \ref{fig:parmats}b-d we show estimates of the parameters corresponding to each of the statistics included in our model of the dyadic intensities $\lambda_{i,j}$.   The intercept estimates, for example, reveal the general propensity at which two blocks tend to communicate.  One salient feature of the parameter estimates is the symmetry in the block structure of the overall communication rates: if a member of group $A$ sends an email to a member of group $B$, the reverse occurs at a similar rate.

However, the asymmetries that the model reveals may often be of particular interest.  An assymetry in intercept estimates between two blocks reveals that for a particular pair of groups that one tends to be the sender and the other tends to be the recipient.  Assymetries for other effects are similarly interpretable.  Consider interactions initiated by a member of block $B_1$ and directed to a member of block $B_2$.  If the estimate for the $\texttt{ab-ba}$ parameter is larger for the set of $(B_1,B_2)$ interactions than for $(B_2,B_1)$ interactions, then the model suggests that those in block $B_2$ tend to respond to emails from those in $B_1$ than vice versa.

@@

\input{../figs/results-llk4.tex}
\input{../figs/results-recall-all.tex}

>>>>

Figure \ref{fig:parmats} uses a fitted model to provide an example of the differences in the dynamics that can exist between two groups of dyads with similar rate of occurrence.  In this particular example we used the University data set and fit the proposed model with an intercept $s_0$, $\texttt{ab-ba}$ effects $s_1$, and $\texttt{ab-by}$ effects $s_3$. {\color{red} In Figure \ref{fig:parmats}a we show the observed number of times each dyadic event occurred over the course of the dataset.   The rows and columns have been sorted according to block membership.  In Figure \ref{fig:parmats}b-d we show estimates of the parameters corresponding to each of the statistics included in our model of the dyadic intensities $\lambda_{i,j}$.   The intercept estimates, for example, reveal the general propensity at which two blocks tend to communicate.

One salient feature of the parameter estimates is the presence of both symmetries and assymmetries in the block structure of the overall communication rates.  For example, if a member of group $A$ sends an email to a member of group $B$, the reverse occurs at a similar rate.  However, the asymmetries that the model reveals may often be of particular interest.  An assymetry in intercept estimates between two blocks reveals that for a particular pair of groups that one tends to be the sender and the other tends to be the recipient.  Assymetries for other effects are similarly interpretable.  Consider interactions initiated by a member of block $B_1$ and directed to a member of block $B_2$.  If the estimate for the $\texttt{ab-ba}$ parameter is larger for the set of $(B_1,B_2)$ interactions than for $(B_2,B_1)$ interactions, then the model suggests that those in block $B_2$ tend to respond to emails from those in $B_1$ than vice versa.

@@

% Tables created by results.r, then hand edited a bit:
% - Added verticle and horizontal lines to make it easier
% - Removed synthetic results
% - Added headers
\input{results-llk4.tex}
\input{results-recall-all.tex}
